### 2018-07-01 Chapters/Chapter1.tex
Bloch Theorem and apendix1

>>>>

The one particle part of the Hamiltonian can be written as:

\begin{equation}
\hat{H}^{(1)}(\textbf{r}) = -\frac{\hbar}{2m}\Delta^2_{\textbf{r}} + U(\textbf{r})
\end{equation}

Where $U(\textbf{r})$ has the symmetry of the lattice, i.e. $U(\textbf{r} + \textbf{R}) = U(\textbf{r})$ for all Bravais lattice vectors $\textbf{R}$(\ref{AP1A}). The group of translation symmetries $T_{\textbf{R}}\phi(\textbf{r}) = \phi(\textbf{r} + \textbf{R})$ is an abelian group, therefore its irreducible representations are one-dimensional, that is, within an energy level $n$ the wavefunctions of that level transform according to the representation they belong: $T_{\textbf{R}}\phi_{n, \textbf{k}}(\textbf{r}) = \Gamma^{\textbf{k}}(\textbf{R}) \phi_{n, \textbf{k}}(\textbf{r})$. Now, imposing periodic boundary conditions, $\phi_{n, \textbf{k}}(\textbf{r} + L_\mu \textbf{a}_\mu) = \Gamma^{\textbf{k}}(L_\mu \textbf{a}_\mu) \phi_{n, \textbf{k}}(\textbf{r}) = \Gamma^{\textbf{k}}(\textbf{a}_\mu)^{L_\mu} \phi_{n, \textbf{k}}(\textbf{r}) = \phi_{n, \textbf{k}}(\textbf{r})$, so that, $\Gamma^{\textbf{k}}(\textbf{a}_\mu)^{L_\mu} = 1$, this can be accomplished if we label the representation with a vector of the first Brillouin zone and have $\Gamma^{\textbf{k}}(R) = e^{i \textbf{k} \textbf{R}}$. Therefore, for a wavefunction in a periodic lattice we have:

\begin{equation}
\phi_{n, \textbf{k}}(\textbf{r}+\textbf{R}) = e^{i\textbf{k}\textbf{R}}\phi_{n, \textbf{k}} (\textbf{r})
\end{equation}

\begin{subappendices}
\begin{section}{Crystal structure and reciprocal lattice}
\label{AP1A}

Here we will introduce some notation. The Bravais lattice in a crystal is the lattice generated by the primitive translations $\textbf{a}_\mu$:

\begin{equation}
\textbf{R} = \sum_{\mu=1}^3 m_\mu \textbf{a}_\mu
\end{equation}

Where $m_\mu$ are integers. The volume of the unit cell is $v = \textbf{a}_1 \cdot (\textbf{a}_2 \times \textbf{a}_3)$. The primitive translations in the reciprocal lattice are defined as $\textbf{b}_1 = \frac{2 \pi}{v}\textbf{a}_2 \times \textbf{a}_3$, etc. With this notation the first Brillouin zone is:

\begin{equation}
\textbf{k} = \sum_{\mu=1}^3 \kappa_\mu \textbf{b}_\mu
\end{equation}

Where $\kappa_\mu = \frac{\nu_\mu}{L_\mu}, -\frac{L_\mu}{2}+1 \leq \nu_\mu \leq \frac{L_\mu}{2}$ so that, $-\frac{1}{2} < \kappa_\mu \leq \frac{1}{2}$. We will only consider cubic lattices where $|\textbf{a}_\mu| = a$ and $|b_\mu| = \frac{2\pi}{a}$ and the vectors of the first Brillouin zone have components $k_\mu = \frac{2 \pi \nu_\mu}{aL}$.

\end{section}
\end{subappendices}
